Bee visitation, pollination services, and plant yield in commodity and hybrid seed canola

### 2022-08-03 Manuscript/main.tex
Moved supplementals to single file
Minor updates to manuscript

All component GLMMs of the pSEM were written in Stan 2.18.1 \citep{gelman2015} and run using \texttt{rstan} 2.26.13.
We used weakly informative normal priors ($\mu=0, \sigma=5$) for fixed effects and gamma priors ($\alpha=1, \beta=1$) for the variance components.
Four separate chains were run with an adaptive phase of 1000 iterations, and a sampling phase of 1000 iterations, then checked for convergence of the chains ($\hat{R} \approx$1) and low autocorrelation within chains (high $N_{eff}$).
We assessed the underlying probability distribution functions of each model using posterior predictive checks \citep{gelman2013}, and found that the probability distributions were properly specified (p$\sim$0.5).
p-values were calculated using the Z-scores (mean/SD) of the sampled posterior distributions; unless otherwise specified, p-values are lower than 0.05 (see Table \ref{tab:commCoef} and \ref{tab:seedCoef} for more detailed model summaries). 
% This means that while the average seed counts (per plant) were unbiased, the variance within a plant was not. 
% However, the negative binomial distribution had the closest posterior predictive checks of any other distribution. 
% Predictions from models are median values of the posterior, representing the median prediction, while intervals displayed in figures are credible intervals (CIs), representing 95\% of the samples drawn from the posterior distribution (analogous to confidence intervals, see \citealt{gelman2013}).

@@

Plant size had by far the strongest positive effect on the number of pods produced (see plant paths in Figure \ref{fig:allSEM}), and there was evidence of pod set suppressing flower production.
Commodity canola plants produced fewer flowers than seed canola plants, and also produced fewer pods per plant overall.
In both commodity and seed canola, plant size had a strong positive effect on the total number of flowers per plant as well as pod set (both p$<$0.001).
Pod set had a strong negative influence on total flowers per plant (p$<$0.0001) in both commodity and seed canola (both p$<<$0.0001), indicating that high pod set suppresses future flower production.
Finally, commodity plants were also lower-yielding (mean: 6.8 g of seeds per plant, SD: 6.0, range: 0.01--47.9) than seed canola plants (mean: 9.6, SD: 7.9, range: 0.02--60.8).
However, the harvest index of commodity canola (mean: 0.26, SD: 0.08, range: 0.005--0.65) was higher than seed canola (mean: 0.23, SD: 0.09, range: 0.003--0.55), meaning that commodity plants produced more seeds per gram of biomass than seed canola plants.%, likely due to the lack of pollen limitation.

@@

\bibliographystyle{humanbio}
\bibliography{references}
%\bibliography{\string{~/Documents/Papers/bibtexRefs/references}}

\clearpage %Supplemental material
\include{extra_supplemental}
% \include{visitors_supplemental}
% \include{models_supplemental}

>>>>

All component GLMMs of the pSEM were written in Stan 2.18.1 \citep{gelman2015} and run using \texttt{rstan} 2.26.13.
We used weakly informative normal priors ($\mu=0, \sigma=5$) for fixed effects and gamma priors ($\alpha=1, \beta=1$) for the variance components.
Four separate chains were run with an adaptive phase of 1000 iterations, and a sampling phase of 1000 iterations, then checked for convergence of the chains ($\hat{R} \approx$1) and low autocorrelation within chains (high $N_{eff}$).
We assessed the underlying probability distribution functions of each model using posterior predictive checks \citep{gelman2013}, and found that the probability distributions were properly specified (p$\sim$0.5).
p-values were calculated using the Z-scores (mean/SD) of the sampled posterior distributions; unless otherwise specified, listed model coefficents have a p-value less than 0.05, and are considered ``strong" effects where p-values are $<0.01$ (see Table \ref{tab:commCoef} and \ref{tab:seedCoef} for more detailed model summaries). 
% This means that while the average seed counts (per plant) were unbiased, the variance within a plant was not. 
% However, the negative binomial distribution had the closest posterior predictive checks of any other distribution. 
% Predictions from models are median values of the posterior, representing the median prediction, while intervals displayed in figures are credible intervals (CIs), representing 95\% of the samples drawn from the posterior distribution (analogous to confidence intervals, see \citealt{gelman2013}).

@@

Plant size had by far the strongest positive effect on the number of pods produced (see plant paths in Figure \ref{fig:allSEM}), and there was evidence of pod set suppressing flower production.
Commodity canola plants produced fewer flowers than seed canola plants, and also produced fewer pods per plant overall (Table \ref{tab:dataSummary}).
In both commodity and seed canola, plant size had a strong positive effect on the total number of flowers per plant as well as pod set.
Pod set had a strong negative influence on total flowers per plant (p$<$0.0001) in both commodity and seed canola (both p$<<$0.0001), indicating that high pod set suppresses future flower production.
Finally, commodity plants were also lower-yielding (mean: 6.8 g of seeds per plant, SD: 6.0, range: 0.01--47.9) than seed canola plants (mean: 9.6, SD: 7.9, range: 0.02--60.8).
However, the harvest index of commodity canola (mean: 0.26, SD: 0.08, range: 0.005--0.65) was higher than seed canola (mean: 0.23, SD: 0.09, range: 0.003--0.55), meaning that commodity plants produced more seeds per gram of biomass than seed canola plants.%, likely due to the lack of pollen limitation.

@@

\bibliographystyle{humanbio}
\bibliography{references}

%Supplemental material
\include{supplemental}
